%------------------------------------------------------------
% DEFINITIONS AND HEADERS -- IGNORE THIS
%------------------------------------------------------------
\documentclass{article}
\usepackage[top=2.2cm, bottom=2.1cm, left=2.2cm, right=2.2cm]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{algpseudocode}
% Get better typography
\usepackage[protrusion=true,expansion=true]{microtype}  
% For algorithms
\usepackage[boxruled,linesnumbered,vlined,inoutnumbered]{algorithm2e}
\SetKwInOut{Parameter}{Parameters}
% For basic math, align, fonts, etc.
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{longtable}
\usepackage{listings}
\lstset{
    basicstyle=\ttfamily,
    breaklines=true,
    columns=flexible
}

\usepackage{mathtools}
\usepackage{mathrsfs}
\usepackage{rotating}
\usepackage{tabularx}
\usepackage{fvextra}
\usepackage{booktabs}
\usepackage{soul}
\usepackage{changepage}
\usepackage{gensymb} % For \degree
\usepackage{lscape}
% For \thead to make line breaks in tables
\usepackage{array}
\usepackage{makecell}
\renewcommand\theadalign{bc}
\renewcommand\theadfont{\bfseries}
\renewcommand\theadgape{\Gape[4pt]}
\renewcommand\cellgape{\Gape[4pt]}
\usepackage{courier} % For \texttt{foo} to put foo in Courier (for code / variables)
\usepackage{lipsum} % For dummy text
% For images
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage[space]{grffile} % For spaces in image names
% For bibliography
\usepackage[round]{natbib}
% For color
\usepackage{xcolor}
\definecolor{light-grey}{rgb}{0.9,0.9,0.9}
\definecolor{dark-red}{rgb}{0.4,0.15,0.15}
\definecolor{dark-blue}{rgb}{0,0,0.7}
\definecolor{darkblue}{rgb}{0,0,.6}
\definecolor{darkred}{rgb}{.58,0,0}
\definecolor{brighterred}{rgb}{.745,0,0}
\definecolor{darkgreen}{rgb}{0,.6,0}
\definecolor{red}{rgb}{.98,0,0}
\usepackage{environ}
% Only show sections in table of contents and rename
\setcounter{tocdepth}{2}
\renewcommand{\contentsname}{Table of Contents}
% For links (e.g., clicking a reference takes you to the phy)
\usepackage{hyperref}
\hypersetup{
    colorlinks, linkcolor={dark-blue},
    citecolor={dark-blue}, urlcolor={dark-blue}
}
\newcommand{\HIGHLIGHT}[1]{\textcolor{blue}{\textbf{#1}}}
% \newcommand{\Solution}[1]{{\color{blue} \paragraph{\bf $\bigstar $ SOLUTION:} { \sf
%     #1} \bigskip}}
\newcommand{\TODO}[1]{\textcolor{blue}{\textbf{{#1}}}}
\newcommand{\POINTS}[1]{\textcolor{purple}{\textbf{{#1}}}}
\providecommand{\mathcolor}[2]{\textcolor{#1}{#2}}
% My definition of "summary boxes" (see below)
\usepackage[most]{tcolorbox}
\definecolor{boxgray}{rgb}{0.95, 0.95, 0.95}
\definecolor{boxblue}{rgb}{0.941, 0.941, 0.98}
\definecolor{boxpink}{rgb}{1.0, 0.93, 0.93}
\definecolor{boxwhite}{rgb}{1.0, 1.0, 1.0}
%\definecolor{boxgreen}{rgb}{0.91, 0.96, 0.9}
\definecolor{boxgreen}{rgb}{0.92, 0.96, 0.92}
\newtcolorbox{mybox}[1][boxwhite]{%
  enhanced,
  boxrule=0.5pt,
  colframe=black,
  colback=#1,
  sharp corners,
  width=\linewidth,
  left=1em,
  right=1em,
  top=0.5em,
  bottom=0.5em,
  boxsep=0pt,
  before skip=1em,
  after skip=0.85em,
}
%------------------------------------------------------------





\begin{document}
%-----------------
%   Homework 4
%-----------------
\newpage
\vspace*{1cm}
\begin{center}
    \begin{Large}
    COMPSCI 589 Final Project - Spring 2026
    \end{Large}
    \\
    \vspace{0.15cm}
    Due \textcolor{darkred}{\textbf{May 8}}, 11:55 pm Eastern Time
\end{center}
\addcontentsline{toc}{subsection}{\textbf{Final Project}}






%-------- Introduction --------------------------

\vspace{0.5cm}
\section*{Introduction}
\vspace{0.5cm}

\begin{itemize}
    \item Each group member was responsible for evaluating the performance of at least one unique algorithm implemented during the semester on each dataset 
    \item The algorithms tested in this project were chosen from the pool of: $k$-NN, Decision Trees, multinomial Naive Bayes, Random Forests, and Neural Networks
    \item All work was done in the shared github repository \url{https://github.com/1985lxw/589_final_project}
    
    \vspace{0.3cm}
    \noindent\rule{\linewidth}{0.5pt}
    \vspace{0.025cm}
    \item \textbf{Katherine} implemented TODO
    \item \textbf{Tiffany} implemented TODO
    \item \textbf{Xing-Wei} implemented TODO
\end{itemize}

% --------------------







\newpage
\noindent {\LARGE{\textbf{Experiments and Analyses}}} 



%------ Experiments and Analyses (i.e., Questions that should be answered) --------------------------
\section{\underline{The Hand-Written Digits Recognition Dataset}}
\subsection{Neural Networks Algorithm}

TODO

\noindent\rule{\textwidth}{0.5pt}

\subsection{Algorithm 2}

TODO 

\noindent\rule{\textwidth}{0.5pt}

\subsection{Algorithm 3}

TODO 

%-------- Extra Credit Questions --------------------------
\newpage
\noindent \textcolor{purple}{\textbf{\Large{Extra Credit}}}
\vspace{0.6cm}

\noindent We did the following extra credit tasks. Describe what you did as part of that task and present the corresponding results. Any source code you develop should be included in your Gradescope submission.




    %---- Extra Credit Question QE.1 ----------------------
    \vspace{1.25cm}
    \noindent \textbf{\HIGHLIGHT{[QE.1] [Extra Credit Question \raisebox{0.2ex}{\scalebox{0.8}{\textnormal{\#}}}1]~(\POINTS{10 Points})}} 
    \vspace{0.3cm}
    
    \noindent You may earn up to 10 extra points if you analyze all four datasets using an additional algorithm. In other
words, you would be evaluating more than two algorithms on each of the datasets discussed in Section 1.

    %---- Extra Credit Question QE.2 ----------------------
    \vspace{1.25cm}
    \noindent \textbf{\HIGHLIGHT{[QE.2] [Extra Credit Question \raisebox{0.2ex}{\scalebox{0.8}{\textnormal{\#}}}2]~(\POINTS{10 Points})}} 
    \vspace{0.3cm}
    
    \noindent You may earn up to 10 extra points if you select a new challenging dataset and evaluate the performance of
different algorithms on it. A challenging dataset should necessarily include both categorical and numerical
attributes and have more than two classes; or it should be a dataset where you have to classify images.




    %---- Extra Credit Question QE.3 ----------------------
    \vspace{1.25cm}
    \noindent \textbf{\HIGHLIGHT{[QE.3] [Extra Credit Question \raisebox{0.2ex}{\scalebox{0.8}{\textnormal{\#}}}3]~(\POINTS{15 Points})}} 
    \vspace{0.3cm}
    
    \noindent You may earn up to 15 extra points if you combine different algorithms and construct an ensemble. For
instance, you could create an ensemble composed of three neural networks (each with a different architecture)
and a random forest. The ensemble would be trained as described in class: each algorithm would be trained
on its own bootstrap dataset, and so on. The final predictions would then be determined by majority voting.
Evaluate your ensemble algorithm on all four datasets discussed in Section 1.

%---- Extra Credit Question QE.4 ----------------------
    \vspace{1.25cm}
    \noindent \textbf{\HIGHLIGHT{[QE.3] [Extra Credit Question \raisebox{0.2ex}{\scalebox{0.8}{\textnormal{\#}}}3]~(\POINTS{15 Points})}} 
    \vspace{0.3cm}

    \noindent You may earn up to 15 extra points if you implement a new type of algorithm—a non-trivial variant of one
of the algorithms studied in class. If you choose to do so, you should evaluate its performance on all four
datasets.

\end{document}